% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\Huge \textbf{Victor Quinn}}
\vspace{.8em}

1616 Sunstone Dr \ \ {$\cdot$}
\ \ McLean, Virginia 22102
\\
(703) 962-7234\ \ {$\cdot$}
\ \ mail@victorquinn.com
\end{center}

\begin{center}
\hrule
\vspace{-0.4em}
\subsection*{Experience}
\end{center}

\begin{itemize}
	\parskip=0.1em
	\item[]
	\headerrow
		{\textbf{NGP VAN}}
		{\textbf{Washington, D.C.}}
	\\
	\headerrow
		{\emph{Senior Software Engineer}}
		{\emph{March 2012 -- Present}}
	\begin{itemize*}
		\item Architecting and writing applications in Node.js with MongoDB or DynamoDB backends. Building and documenting RESTful APIs for these apps, and having each app consume the APIs of the others and of other core systems within our company to build out a very powerful network of systems to handle interactions with the public. 
		\item These applications have been deployed at very large-scale across NGP VAN's large client-base and some stood up to the high stakes/high load environment of the 2012 election across presidential, senate, and smaller races.
		\item These apps are used for tracking user interactions with our public facing products, for accepting data, for processing payments for contributions, and performing analytics. 
		\item Currently leading an agile team (3 Developers, 1 Product Manager, and 1 Quality Assurance) to architect and implement these apps in a scrum environment using Jira.
		\item Led projects with a team split, half in Boston, half in D.C. to greatly simplify API interactions, to move mechanics client-side where feasible using Backbone and Angular for greater separation of concerns, better, more snappy user experience, to move the team toward test driven development, and to centrally integrate multiple core internal backend systems
		\item Latest accomplishment was leading a rewrite of our system for taking contributions, moving from very server-side heavy code to a powerful client-side single page app with rich interactions to process payments contributions and other CRM data which talks directly to a new REST API I architected onto the company's core financial database.
	\end{itemize*}

	\item[]
	\headerrow
		{\textbf{Amherst College}}
		{\textbf{Amherst, MA}}
	\\
	\headerrow
		{\emph{Web Programmer}}
		{\emph{2008 -- March 2012}}
	\begin{itemize*}
		\item Specialized in web development in PHP and JavaScript on a Drupal stack, tying into a MySQL database
		\item Collaborated with a team of developers to create custom tools in order to allow faculty and staff to create rich content for education
		\item As the User Interface expert on the team, focused on maximizing ease of use through interface design
		\item Nature of the job required knowledge of the entire IT stack including servers, redundant backups, databases, storage solutions, uptime monitoring, and technologies like Apache and Linux server administration
	\end{itemize*}

	\item[]
	\headerrow
		{\textbf{University of Massachusetts Amherst}}
		{\textbf{Amherst, MA}}
	\\
	\headerrow
		{\emph{Senior Developer and Backup Systems Administrator}}
		{\emph{2005 -- 2008}}
	\begin{itemize*}
		\item Specialized in software design for internal processes including, but not limited to, web development, custom Windows application development, and other various scripting
		\item As the Backup Systems Administrator, gained extensive knowledge on the entire server architecture
	\end{itemize*}

\end{itemize}

\begin{center}
\hrule
\vspace{-0.4em}
\subsection*{Education}
\end{center}

\begin{itemize}
	\parskip=0.1em

	\item[]
	\headerrow
		{\textbf{Western New England University}}
		{\textbf{Springfield, MA}}
	\\
	\headerrow
		{\emph{School of Law, Juris Doctor Degree}}
		{\emph{2007 -- 2011}}
	\begin{itemize*}
		\item Attended part-time at night while working full-time as a computer programmer during the day
		\item As President of the Intellectual Property Law Association, organized multiple IP awareness events
		\item Course concentration in Intellectual Property Law including an Independent Study in Patent Litigation
		\item Awarded two CALI Excellence for the Future Awards for the Highest Achievement in Analytical Methods for Lawyers and Trademark Law
	\end{itemize*}

	\item[]
	\headerrow
		{\textbf{University of Massachusetts Amherst}}
		{\textbf{Amherst, MA}}
	\\
	\headerrow
		{\emph{College of Natural Sciences and Mathematics, B.S. Physics and B.S. Computer Science}}
		{\emph{2001 -- 2006}}
	\begin{itemize*}
		\item Completed Double Bachelor of Science Degree Program
		\item Served as a New Students Program counselor, helping ease student transition to the University and as a leader for the wilderness orientation program
		\item Member of the Computer Science Talent Advancement Program
		\item Computer Science Mentor
	\end{itemize*}
\end{itemize}

\begin{center}
\hrule
\subsection*{Programming Skills}
\end{center}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Infrastructures:]
	Expert knowledge of computers, including full IT backend. More than five years experience as a Linux systems admin.
	\item[Computer Language Skills:]
	Expert in JavaScript and PHP, capable in \LaTeX, Perl, Python, Ruby, Objective-C (iOS), shell scripts, SQL, Lisp, etc.
	\item[CMS and Framework Experience:]
	Guru level familiarity with Drupal, some experience with other open-source CMS's such as Joomla, WordPress. Lot of experience with Express, some experience with other web frameworks like Django, Ruby on Rails, Sinatra, and Meteor. Personal website (http://victorquinn.com) is created using OctoPress.
	\item[SaaS/PaaS Experience:]
	Lot of experience using hosted services for developing and hosting large scale apps. SaaS experience includes setup/management/configuration of Google Apps, FastMail, GitHub, Hipchat, Jira, Trello, and others. For deploying large scale apps, experience includes Linode, Heroku, Amazon AWS assets (S3, DynamoDB, CloudFront, Route53, EC2, RDS, Glacier, and more), MailChimp and Mandrill.
	\item[Version Control:]
	Expert in git, have worked with subversion as well. Have given training courses on git to multiple groups.
\end{description*}
\end{indentsection}

\begin{center}
\hrule
\vspace{-0.4em}
\subsection*{Open Source Projects}
\end{center}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Chance:]
	Created this library to help generate random things in JavaScript. Useful for the browser or Node.js for automated tests, stub data, etc. Gained more than 250 stars in less than a month on GitHub. http://chancejs.com
	\item[Backbone.CrossDomain:]
         Created this plugin which is an AMD compatible drop-in replacement for Backbone's core sync function which extends it to allow CORS requests in IE7/8/9 which Backbone does not support out of the box for cross domain requests. https://github.com/victorquinn/Backbone.CrossDomain
	\item[Ubercart Stripe Module:]
	 Developed a module for Drupal's most popular e-commerce system using the Stripe payment processor. Their API was a dream to work with. http://drupal.org/project/uc\_stripe
	\item[DuckDuckGo Safari Extension:]
	I enjoyed using DuckDuckGo, a search engine which is positioning itself as a more privacy-friendly alternative to Google, so when Apple first released its Extensions for Safari, I jumped at the opportunity to write this Extension.  https://extensions.apple.com
	\item[Alfred Volume Extension:]
	Alfred is one of my must-haves and is used to control almost everything on my system, but one thing it didn't do was control my volume -- so I set forth to change that by developing the Alfred Volume Extension. https://gist.github.com/1794961
	\item[Theme Hider:]
	Starting from a base and solving a seemingly simple problem in Drupal that heretofore went without a solution, I wrote a Drupal module to allow an admin user to selectively hide themes from other users. http://drupal.org/project/theme\_hider
	\item[Monster Menus:]
	A project begun by Amherst College to deal with inadequacies in granular permissions in Drupal, I have made substantial contributions to this now open source project, both during my tenure at Amherst and after. http://drupal.org/project/monster\_menus
\end{description*}
\end{indentsection}

\begin{center}
\hrule
\vspace{-0.4em}
\subsection*{Miscellaneous}
\end{center}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[U.S. Patent and Trademark Office:]
	Registered Patent Agent -- Registration Number: 69321
	\item[Other:]
	Avid outdoorsman and traveler. Motorcyclist who commutes daily on a Harley-Davidson. Hobbies include tinkering with emerging web technologies, video editing, graphic design, homebrew, and the art of letterpress. Achieved the rank of Eagle Scout on January, 2000.
	\item[Reading List:]
	HackerNews, DailyJS, Echo JS, TheVerge, Marco.org, DaringFireball, Alex Maccaw's Blog
\end{description*}
\end{indentsection}

\end{document}
